\tool: Revisiting BadUSB with Type-C

### 2021-03-10 WOOT/Files/badusb.tex
fix typo

When running in this mode, \tool passively processes the victim's video stream
and detects ``valuable'' private data.  The data is considered as
``valuable'' or not by a customized detector. We implemented a simple
payment code detector for the poof-of-concept purpose, which demonstrates that we successfully transfer money from a victim to an
attacker. More detail can be obtained in Section~\ref{sec:experiment}.

>>>>

When running in this mode, \tool passively processes the victim's video stream
and detects ``valuable'' private data.  The data is considered as
``valuable'' or not by a customized detector. We implemented a simple
payment code detector for the proof-of-concept purpose, which demonstrates that we successfully transfer money from a victim to an
attacker. More detail can be obtained in Section~\ref{sec:experiment}.
